Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-05-24 doc/paper.Rmd
small edits

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{rlrrr}
  \hline
Method & Data Source & False Positives & False Negatives\\
  \hline
Consecutive Matching Bullets Striae (CMS) & & & \\ \textbf{\citet{aoas}} &  & 6.25\% &  33.851\% \\ \hline
Consecutive Non-matching Striae (CNMS) & Bullets & & \\  \textbf{\citet{aoas}} & & 6.26\% & 35.4166\%  \\ \hline
Average Distance (D) & Bullets  &  & \\ \textbf{\citet{aoas}} & & 6.25\% & 45.833\% \\ \hline 
Cross-correlation Function (CCF) & Bullets & & \\ \textbf{\citet{aoas}}  & & 6.25\% & 17.7083\%  \\ \hline
Sum of Peaks (S) & Bullets  & & \\  \textbf{\citet{aoas}} & & 6.25\% &  18.22915\% \\
   \hline
\end{tabular}}
\caption{\label{tab:bullets-ER} Error Rates in same-source bullet analysis reported in the literature.}
\end{table}

>>>>

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{rlrrr}
  \hline
Method & Data Source & False Positives & False Negatives\\
  \hline
Consecutive Matching Bullets Striae (CMS) & Bullets & & \\ \textbf{\citet{aoas}} &  & 6.25\% &  33.851\% \\ \hline
Consecutive Non-matching Striae (CNMS) & Bullets & & \\  \textbf{\citet{aoas}} & & 6.26\% & 35.4166\%  \\ \hline
Average Distance (D) & Bullets  &  & \\ \textbf{\citet{aoas}} & & 6.25\% & 45.833\% \\ \hline 
Cross-correlation Function (CCF) & Bullets & & \\ \textbf{\citet{aoas}}  & & 6.25\% & 17.7083\%  \\ \hline
Sum of Peaks (S) & Bullets  & & \\  \textbf{\citet{aoas}} & & 6.25\% &  18.22915\% \\
   \hline
\end{tabular}}
\caption{\label{tab:bullets-ER} Error Rates in same-source bullet analysis reported in the literature.}
\end{table}
